### 2018-04-20 paper/main.tex
Paper template

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Paper Title*\\
{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
should not be used}
\thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
}

\maketitle

\begin{abstract}
This document is a model and instructions for \LaTeX.
This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
or Math in Paper Title or Abstract.
\end{abstract}

\begin{IEEEkeywords}
component, formatting, style, styling, insert
\end{IEEEkeywords}

\section{Introduction}
This document is a model and instructions for \LaTeX.
Please observe the conference page limits.

\section{Ease of Use}

\subsection{Maintaining the Integrity of the Specifications}

The IEEEtran class file is used to format your paper and style the text. All margins, 
column widths, line spaces, and text fonts are prescribed; please do not 
alter them. You may note peculiarities. For example, the head margin
measures proportionately more than is customary. This measurement 
and others are deliberate, using specifications that anticipate your paper 
as one part of the entire proceedings, and not as an independent document. 
Please do not revise any of the current designations.

\section{Prepare Your Paper Before Styling}
Before you begin to format your paper, first write and save the content as a 
separate text file. Complete all content and organizational editing before 
formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
proofreading, spelling and grammar.

Keep your text and graphic files separate until after the text has been 
formatted and styled. Do not number text heads---{\LaTeX} will do that 
for you.

\subsection{Abbreviations and Acronyms}\label{AA}
Define abbreviations and acronyms the first time they are used in the text, 
even after they have been defined in the abstract. Abbreviations such as 
IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
abbreviations in the title or heads unless they are unavoidable.

\subsection{Units}
\begin{itemize}
\item Use either SI (MKS) or CGS as primary units. (SI units are encouraged.) English units may be used as secondary units (in parentheses). An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds. This often leads to confusion because equations do not balance dimensionally. If you must use mixed units, clearly state the units for each quantity that you use in an equation.
\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''. Spell out units when they appear in text: ``. . . a few henries'', not ``. . . a few H''.
\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
\end{itemize}

\subsection{Equations}
Number equations consecutively. To make your 
equations more compact, you may use the solidus (~/~), the exp function, or 
appropriate exponents. Italicize Roman symbols for quantities and variables, 
but not Greek symbols. Use a long dash rather than a hyphen for a minus 
sign. Punctuate equations with commas or periods when they are part of a 
sentence, as in:
\begin{equation}
a+b=\gamma\label{eq}
\end{equation}

Be sure that the 
symbols in your equation have been defined before or immediately following 
the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
the beginning of a sentence: ``Equation \eqref{eq} is . . .''

\subsection{\LaTeX-Specific Advice}

Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
of ``hard'' references (e.g., \verb|(1)|). That will make it possible
to combine sections, add equations, or change the order of figures or
citations without having to go through the file line by line.

Please don't use the \verb|{eqnarray}| equation environment. Use
\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
environment leaves unsightly spaces around relation symbols.

Please note that the \verb|{subequations}| environment in {\LaTeX}
will increment the main equation counter even when there are no
equation numbers displayed. If you forget that, you might write an
article in which the equation numbers skip from (17) to (20), causing
the copy editors to wonder if you've discovered a new method of
counting.

{\BibTeX} does not work by magic. It doesn't get the bibliographic
data from thin air but from .bib files. If you use {\BibTeX} to produce a
bibliography you must send the .bib files.

{\LaTeX} can't read your mind. If you assign the same label to a
subsubsection and a table, you might find that Table I has been cross
referenced as Table IV-B3.

{\LaTeX} does not have precognitive abilities. If you put a
\verb|\label| command before the command that updates the counter it's
supposed to be using, the label will pick up the last counter to be
cross referenced instead. In particular, a \verb|\label| command
should not go before the caption of a figure or a table.

Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
will not stop equation numbers inside \verb|{array}| (there won't be
any anyway) and it might stop a wanted equation number in the
surrounding equation.

\subsection{Some Common Mistakes}\label{SCM}
\begin{itemize}
\item The word ``data'' is plural, not singular.
\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation. When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks. A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this). (A parenthetical sentence is punctuated within the parentheses.)
\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
\item Do not confuse ``imply'' and ``infer''.
\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
\end{itemize}
An excellent style manual for science writers is \cite{b7}.

\subsection{Authors and Affiliations}
\textbf{The class file is designed for, but not limited to, six authors.} A 
minimum of one author is required for all conference articles. Author names 
should be listed starting from left to right and then moving down to the 
next line. This is the author sequence that will be used in future citations 
and by indexing services. Names should not be listed in columns nor group by 
affiliation. Please keep your affiliations as succinct as possible (for 
example, do not differentiate among departments of the same organization).

\subsection{Identify the Headings}
Headings, or heads, are organizational devices that guide the reader through 
your paper. There are two types: component heads and text heads.

Component heads identify the different components of your paper and are not 
topically subordinate to each other. Examples include Acknowledgments and 
References and, for these, the correct style to use is ``Heading 5''. Use 
``figure caption'' for your Figure captions, and ``table head'' for your 
table title. Run-in heads, such as ``Abstract'', will require you to apply a 
style (in this case, italic) in addition to the style provided by the drop 
down menu to differentiate the head from the text.

Text heads organize the topics on a relational, hierarchical basis. For 
example, the paper title is the primary text head because all subsequent 
material relates and elaborates on this one topic. If there are two or more 
sub-topics, the next level head (uppercase Roman numerals) should be used 
and, conversely, if there are not at least two sub-topics, then no subheads 
should be introduced.

\subsection{Figures and Tables}
\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
bottom of columns. Avoid placing them in the middle of columns. Large 
figures and tables may span across both columns. Figure captions should be 
below the figures; table heads should appear above the tables. Insert 
figures and tables after they are cited in the text. Use the abbreviation 
``Fig.~\ref{fig}'', even at the beginning of a sentence.

\begin{table}[htbp]
\caption{Table Type Styles}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
\cline{2-4} 
\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
\hline
copy& More table copy$^{\mathrm{a}}$& &  \\
\hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
\end{tabular}
\label{tab1}
\end{center}
\end{table}

\begin{figure}[htbp]
\caption{Example of a figure caption.}
\label{fig}
\end{figure}

Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
rather than symbols or abbreviations when writing Figure axis labels to 
avoid confusing the reader. As an example, write the quantity 
``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
units in the label, present them within parentheses. Do not label axes only 
with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
quantities and units. For example, write ``Temperature (K)'', not 
``Temperature/K''.

\section*{Acknowledgment}

The preferred spelling of the word ``acknowledgment'' in America is without 
an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
acknowledgments in the unnumbered footnote on the first page.

\section*{References}

Please number citations consecutively within brackets \cite{b1}. The 
sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''

Number footnotes separately in superscripts. Place the actual footnote at 
the bottom of the column in which it was cited. Do not put footnotes in the 
abstract or reference list. Use letters for table footnotes.

Unless there are six authors or more give all authors' names; do not use 
``et al.''. Papers that have not been published, even if they have been 
submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
Capitalize only the first word in a paper title, except for proper nouns and 
element symbols.

For papers published in translation journals, please give the English 
citation first, followed by the original foreign-language citation \cite{b6}.

\end{document}

### 2018-04-20 paper/main.tex
define sections

@@
 
-\title{Paper Title*\\
-{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
-should not be used}
-\thanks{Identify applicable funding agency here. If none, delete this.}
+\title{Activity Recognition with mobile devices*\\
 }
 
-\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address}
+\author{\IEEEauthorblockN{1\textsuperscript{st} Simon Angerbauer}
+\IEEEauthorblockA{\textit{Mobile Computing} \\
+\textit{University Of Applied Sciences Upper Austria}\\
+Hagenberg, Austria \\
+simon.angerbauer@students.fh-hagenberg.at}
 \and
-\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address}
+\IEEEauthorblockN{2\textsuperscript{nd} Paul Schmutz}
+\IEEEauthorblockA{\textit{Mobile Computing} \\
+\textit{University Of Applied Sciences Upper Austria}\\
+Hagenberg, Austria \\
+paul.schmutz@students.fh-hagenberg.at}
 \and
-\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address}
-\and
-\IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address}
-\and
-\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address}
-\and
-\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address}
+\IEEEauthorblockN{3\textsuperscript{rd} Roman Socovka}
+\IEEEauthorblockA{\textit{Mobile Computing} \\
+\textit{University Of Applied Sciences Upper Austria}\\
+Hagenberg, Austria \\
+roman.socovka@students.fh-hagenberg.at}
 }
@@
 \section{Introduction}
-This document is a model and instructions for \LaTeX.
-Please observe the conference page limits.
+intro
 
-\section{Ease of Use}
+\section{Activity Recoginition}
 
-\subsection{Maintaining the Integrity of the Specifications}
+\section{Related Work}
 
-The IEEEtran class file is used to format your paper and style the text. All margins, 
-column widths, line spaces, and text fonts are prescribed; please do not 
-alter them. You may note peculiarities. For example, the head margin
-measures proportionately more than is customary. This measurement 
-and others are deliberate, using specifications that anticipate your paper 
-as one part of the entire proceedings, and not as an independent document. 
-Please do not revise any of the current designations.
+\subsection{Subsection blabla}
 
-\section{Prepare Your Paper Before Styling}
-Before you begin to format your paper, first write and save the content as a 
-separate text file. Complete all content and organizational editing before 
-formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
-proofreading, spelling and grammar.
+subsection
 
-Keep your text and graphic files separate until after the text has been 
-formatted and styled. Do not number text heads---{\LaTeX} will do that 
-for you.
+\section{Evaluation}
 
-\subsection{Abbreviations and Acronyms}\label{AA}
-Define abbreviations and acronyms the first time they are used in the text, 
-even after they have been defined in the abstract. Abbreviations such as 
-IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
-abbreviations in the title or heads unless they are unavoidable.
+\subsection{Results}
 
-\subsection{Units}
-\begin{itemize}
-\item Use either SI (MKS) or CGS as primary units.
-(SI units are encouraged.) English units may be used as secondary units (in parentheses).
-An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
-\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds.
-This often leads to confusion because equations do not balance dimensionally.
-If you must use mixed units, clearly state the units for each quantity that you use in an equation.
-\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''.
-Spell out units when they appear in text: ``.
-.
-.
-a few henries'', not ``.
-.
-.
-a few H''.
-\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
-\end{itemize}
+TODO Charts oder shit
 
-\subsection{Equations}
-Number equations consecutively. To make your 
-equations more compact, you may use the solidus (~/~), the exp function, or 
-appropriate exponents. Italicize Roman symbols for quantities and variables, 
-but not Greek symbols. Use a long dash rather than a hyphen for a minus 
-sign. Punctuate equations with commas or periods when they are part of a 
-sentence, as in:
-\begin{equation}
-a+b=\gamma\label{eq}
-\end{equation}
+\subsection{Analysis}
 
-Be sure that the 
-symbols in your equation have been defined before or immediately following 
-the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
-the beginning of a sentence: ``Equation \eqref{eq} is . . .''
+TODO some analysis shit
 
-\subsection{\LaTeX-Specific Advice}
+\section{Conclusion}
 
-Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
-of ``hard'' references (e.g., \verb|(1)|). That will make it possible
-to combine sections, add equations, or change the order of figures or
-citations without having to go through the file line by line.
-
-Please don't use the \verb|{eqnarray}| equation environment. Use
-\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
-environment leaves unsightly spaces around relation symbols.
-
-Please note that the \verb|{subequations}| environment in {\LaTeX}
-will increment the main equation counter even when there are no
-equation numbers displayed. If you forget that, you might write an
-article in which the equation numbers skip from (17) to (20), causing
-the copy editors to wonder if you've discovered a new method of
-counting.
-
-{\BibTeX} does not work by magic. It doesn't get the bibliographic
-data from thin air but from .bib files. If you use {\BibTeX} to produce a
-bibliography you must send the .bib files.
-
-{\LaTeX} can't read your mind. If you assign the same label to a
-subsubsection and a table, you might find that Table I has been cross
-referenced as Table IV-B3.
-
-{\LaTeX} does not have precognitive abilities. If you put a
-\verb|\label| command before the command that updates the counter it's
-supposed to be using, the label will pick up the last counter to be
-cross referenced instead. In particular, a \verb|\label| command
-should not go before the caption of a figure or a table.
-
-Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
-will not stop equation numbers inside \verb|{array}| (there won't be
-any anyway) and it might stop a wanted equation number in the
-surrounding equation.
-
-\subsection{Some Common Mistakes}\label{SCM}
-\begin{itemize}
-\item The word ``data'' is plural, not singular.
-\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
-\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation.
-When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks.
-A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this).
-(A parenthetical sentence is punctuated within the parentheses.)
-\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
-\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
-\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
-\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
-\item Do not confuse ``imply'' and ``infer''.
-\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
-\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
-\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
-\end{itemize}
-An excellent style manual for science writers is \cite{b7}.
-
-\subsection{Authors and Affiliations}
-\textbf{The class file is designed for, but not limited to, six authors.} A 
-minimum of one author is required for all conference articles. Author names 
-should be listed starting from left to right and then moving down to the 
-next line. This is the author sequence that will be used in future citations 
-and by indexing services. Names should not be listed in columns nor group by 
-affiliation. Please keep your affiliations as succinct as possible (for 
-example, do not differentiate among departments of the same organization).
-
-\subsection{Identify the Headings}
-Headings, or heads, are organizational devices that guide the reader through 
-your paper. There are two types: component heads and text heads.
-
-Component heads identify the different components of your paper and are not 
-topically subordinate to each other. Examples include Acknowledgments and 
-References and, for these, the correct style to use is ``Heading 5''. Use 
-``figure caption'' for your Figure captions, and ``table head'' for your 
-table title. Run-in heads, such as ``Abstract'', will require you to apply a 
-style (in this case, italic) in addition to the style provided by the drop 
-down menu to differentiate the head from the text.
-
-Text heads organize the topics on a relational, hierarchical basis. For 
-example, the paper title is the primary text head because all subsequent 
-material relates and elaborates on this one topic. If there are two or more 
-sub-topics, the next level head (uppercase Roman numerals) should be used 
-and, conversely, if there are not at least two sub-topics, then no subheads 
-should be introduced.
-
-\subsection{Figures and Tables}
-\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
-bottom of columns. Avoid placing them in the middle of columns. Large 
-figures and tables may span across both columns. Figure captions should be 
-below the figures; table heads should appear above the tables. Insert 
-figures and tables after they are cited in the text. Use the abbreviation 
-``Fig.~\ref{fig}'', even at the beginning of a sentence.
-
-\begin{table}[htbp]
-\caption{Table Type Styles}
-\begin{center}
-\begin{tabular}{|c|c|c|c|}
-\hline
-\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
-\cline{2-4} 
-\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
-\hline
-copy& More table copy$^{\mathrm{a}}$& &  \\
-\hline
-\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
-\end{tabular}
-\label{tab1}
-\end{center}
-\end{table}
-
-\begin{figure}[htbp]
-\caption{Example of a figure caption.}
-\label{fig}
-\end{figure}
-
-Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
-rather than symbols or abbreviations when writing Figure axis labels to 
-avoid confusing the reader. As an example, write the quantity 
-``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
-units in the label, present them within parentheses. Do not label axes only 
-with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
-\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
-quantities and units. For example, write ``Temperature (K)'', not 
-``Temperature/K''.
-
-\section*{Acknowledgment}
-
-The preferred spelling of the word ``acknowledgment'' in America is without 
-an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
-G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
-acknowledgments in the unnumbered footnote on the first page.
+TODO Conclude or smth
 
@@
 
-Please number citations consecutively within brackets \cite{b1}. The 
-sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
-number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
-the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''
-
-Number footnotes separately in superscripts. Place the actual footnote at 
-the bottom of the column in which it was cited. Do not put footnotes in the 
-abstract or reference list. Use letters for table footnotes.
-
-Unless there are six authors or more give all authors' names; do not use 
-``et al.''. Papers that have not been published, even if they have been 
-submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
-that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
-Capitalize only the first word in a paper title, except for proper nouns and 
-element symbols.
-
-For papers published in translation journals, please give the English 
-citation first, followed by the original foreign-language citation \cite{b6}.
-
 \end{document}

### 2018-04-30 paper/main.tex
zuteilung
Bibliography

@@
 % The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
+
 \usepackage{cite}
@@
 \usepackage{algorithmic}
+\usepackage[printonlyused]{acronym}
 \usepackage{graphicx}
 \usepackage{textcomp}
+%\usepackage[backend=bibtex,style=IEEEtr]{biblatex}
+
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 
-\title{Activity Recognition with mobile devices*\\
+\title{Activity Recognition with mobile devices\\
 }
@@
 or Math in Paper Title or Abstract.
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+TODO
 \end{abstract}
@@
 
-\section{Introduction}
+\section{Introduction -- Simon}
+asdfas
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
 intro
 
-\section{Activity Recoginition}
-
-\section{Related Work}
-
+\section{Related Work -- Paul}
+Refer to articles, how they collected data
+did they use mobile phones or separate acceleration sensor devices
+body placement of the sensor
+The experimental results show that when the sensor is placed on different rigid body, different models are required for certain activities ~\cite{Henpraserttae2011}.
 \subsection{Subsection blabla}
@@
 
-\section{Evaluation}
+\section{Evaluation -- Simon}
 
 \subsection{Results}
-
+TODO add image
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
 TODO Charts oder shit
@@
 
-\section{Conclusion}
+\section{Conclusion -- Paul}
 
@@
 
-\section*{References}
+\section*{List of Abbreviations}
+\begin{acronym}[XXXXXXXX]
+ \acro{HAR}{Human Activity Recognition}
+\end{acronym}
+ias
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+
+TODO Abbreviations
+
+\addcontentsline{toc}{section}{References}
+\bibliographystyle{unsrt}
+\bibliography{references}
+asdfiajsd
+%%%----------------------------------------------------------
+%\MakeBibliography                        				% references
+%%%----------------------------------------------------------
+%\printbibliography
+%\bibliography{references}  	% name of bibliography file (references.bib)
+%\bibliographystyle{ieeetr}
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+TODO Refs
 

### 2018-04-30 paper/main.tex
Related work

@@
 \begin{IEEEkeywords}
-component, formatting, style, styling, insert
+Human Activity Recognition, accelerometer, movement pattern detection
 \end{IEEEkeywords}
@@
 \section{Related Work -- Paul}
+blbla
 Refer to articles, how they collected data
@@
 body placement of the sensor
+significant difference of the results with varying orientation of the phone/sensor.
+As the performance of algorithms and devices have increased, these problems can be dealt with by now.
+Also wearing the sensor at different body parts is worsening the situation.
+Therefore a training phase combined with an AI learning algorithm can help to improve detection results.
+Kwapisz2011 ~\cite{Kwapisz2011} however is using orientation of the 3 tri-axial sensor to distinguish between standing and sitting, which is not a real-world scenario for everybody as every individual user might carry the phone in a different way.
+results are more precise with multiple sensors, but cell phones are the easiest solution to spread the capability of measuring and classifying movement patterns
+real-time processing at low cost ~\cite{Brezmes2009}
 The experimental results show that when the sensor is placed on different rigid body, different models are required for certain activities ~\cite{Henpraserttae2011}.
+bla
 \subsection{Subsection blabla}
-
 subsection
@@
  \acro{HAR}{Human Activity Recognition}
+ \acro{AI}{Artificial Intelligence}
 \end{acronym}

### 2018-05-24 paper/main.tex
add images
Related work, conclusion

--- 2018-04-30 paper/main.tex
@@
 \section{Related Work -- Paul}
+As activity recognition is a popular topic, there already many studies and papers recording detection of gestures in both natural and laboratory settings as well as using regular mobile accelerometers and multiple high-performant accelerometers attached to different parts of the body.
+Although the use of multiple separate acceleration sensor devices can improve results drastically up to 80\% and more ~\cite{Bao2004}, cell phones are the easiest solution to spread the capability of measuring and classifying movement patterns.
+The use of smartphone sensors is not only practicable but also allows developing applications at low-cost ~\cite{Brezmes2009}.
+Cell phones however are disadvantageous to the effect that the device tilt is uncertain oftentimes ~\cite{Brezmes2009}.
+So sensor data for a particular movement patterns may differ from each other significantly.
+Under that circumstance algorithms therefore are far more complex and their results more inaccurate.
+As the performance of algorithms and devices have increased, these problems can be dealt with by now.
+Also wearing the sensor at different body parts is worsening the situation.
+Therefore a training phase combined with an AI learning algorithm can help to improve detection results ~\cite{Kwapisz2011,Bao2004}.
+While multi-sensor approaches focus on detecting a large set of activities ~\cite{Bao2004}, many studies that make use of just one triaxial smartphone accelerometer are concentrating on a smaller subset like walking, jogging, ascending stairs, descending stairs, sitting and standing which is sufficient for detecting standard activities of most people's everyday lives.
+
 Refer to articles, how they collected data
-did they use mobile phones or separate acceleration sensor devices
 body placement of the sensor
+Kwapisz2011 ~\cite{Kwapisz2011} however is using orientation of the 3 tri-axial sensor to distinguish between standing and sitting, which is not a real-world scenario for everybody as every individual user might carry the phone in a different way.
+real-time processing at low cost ~\cite{Brezmes2009}
 The experimental results show that when the sensor is placed on different rigid body, different models are required for certain activities ~\cite{Henpraserttae2011}.
-\subsection{Subsection blabla}
-
-subsection
-
-\section{Evaluation -- Simon}
-
-\subsection{Results}
-TODO add image
+bla
 \\
@@
 \\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-TODO Charts oder shit
+\subsection{Subsection blabla}
+subsection
+\newpage
+\section{Evaluation -- Simon}
 
+\subsection{Results}
+\begin{figure}[!htb]
+  \includegraphics[width=\linewidth]{walking.png}
+  \caption{Walking}
+  \label{fig:walking}
+\end{figure}
+\begin{figure}[!htb]
+  \includegraphics[width=\linewidth]{jogging.png}
+  \caption{Jogging}
+  \label{fig:jogging}
+\end{figure}
+\begin{figure}[!htb]
+  \includegraphics[width=\linewidth]{sitting.png}
+  \caption{Sitting}
+  \label{fig:sitting}
+\end{figure}
+\begin{figure}[!htb]
+  \includegraphics[width=\linewidth]{standing.png}
+  \caption{Standing}
+  \label{fig:standing}
+\end{figure}
+\begin{figure}[!htb]
+  \includegraphics[width=\linewidth]{ascending_stairs.png}
+  \caption{Ascending Stairs}
+  \label{fig:ascendingStairs}
+\end{figure}
+\begin{figure}[!htb]
+  \includegraphics[width=\linewidth]{descending_stairs.png}
+  \caption{Descending Stairs}
+  \label{fig:descendingStairs}
+\end{figure}
+
+\newpage
 \subsection{Analysis}
@@
 \section{Conclusion -- Paul}
+The use of smartphones for activity recognition is appropriate to achieve a high number of users, however it not the most accurate approach.
+Smart wearable devices are getting more popular, which could allow the use of multiple sensors increasing accuracy of gesture detection.
+As there is a large variety of such wearables and the majority still owns one single cell smartphone, attaching multiple accelerometers  on different parts of the body generally is not a natural use-case.
+We think that focusing on a high number of users by concentrating on evaluating just smartphone sensor data is significant, as the goal is to give as many people as possible access to the technology of activity recognition.
+Cell phone accelerometer data still can be enhanced by developing more sophisticated software processing sensor data and learning user behaviours, so that a basic set of gestures like walking, standing or climbing stairs can be detected mainting a low error rate while keeping the number of users at an upper level.
 
-TODO Conclude or smth
+Could be important for the health, aging, monitoring people under medical control
 

### 2018-05-24 paper/main.tex
Related work, conclusion

@@
 Under that circumstance algorithms therefore are far more complex and their results more inaccurate.
-As the performance of algorithms and devices have increased, these problems can be dealt with by now.
+In one approach for instance the orientation of the 3 tri-axial sensor is used to distinguish between standing and sitting ~\cite{Kwapisz2011}, which is not a real-world scenario for everybody as every individual user might carry the phone in a different way.
+As the performance of algorithms and devices have increased, the problems of phone orientation can be dealt with by now.
 Also wearing the sensor at different body parts is worsening the situation.
 Therefore a training phase combined with an AI learning algorithm can help to improve detection results ~\cite{Kwapisz2011,Bao2004}.
+Most studies discussing activity recognition with mobile devices usually introduce training phases for collecting sensor data.
+For example each individual user has a preferred way to hold the phone, like a chest pocket, front trousers pocket, a rear trousers pocket, an inner jacket pocket, \dots ~\cite{Brezmes2009}.
+This is essential as different sensor placement on the body produce different acceleration data.
+The experimental results show that when the sensor is placed on different rigid body, different models are required for certain activities ~\cite{Henpraserttae2011}.
 While multi-sensor approaches focus on detecting a large set of activities ~\cite{Bao2004}, many studies that make use of just one triaxial smartphone accelerometer are concentrating on a smaller subset like walking, jogging, ascending stairs, descending stairs, sitting and standing which is sufficient for detecting standard activities of most people's everyday lives.
+A critical point is real-time detection of gestures.
+Analyzing data beforehand is necessary in order to recognize certain movement patterns.
+Real-time capability of systems can be essential for detecting running in a sports and health application or even monitoring aged people or anyone under medical control ~\cite{Brezmes2009}.
+Today's mobile devices have enough computing power to collect and detect for example a fall which as a emergency requires fast reaction.
+The solution of handling calculations on the mobile device is also highly scalable as no additional server is necessary for data processing ~\cite{Kwapisz2011}.
+As mobile devices nowadays are highly connective and come with additional sensors such as GPS sensors, vision sensors, audio sensors, light sensors, temperature sensors or direction sensors ~\cite{Kwapisz2011}, activity recognition offers even more possibilities.
+The availability of these technologies creates new data mining opportunities ~\cite{Kwapisz2011}.
 
-Refer to articles, how they collected data
-body placement of the sensor
-Kwapisz2011 ~\cite{Kwapisz2011} however is using orientation of the 3 tri-axial sensor to distinguish between standing and sitting, which is not a real-world scenario for everybody as every individual user might carry the phone in a different way.
-real-time processing at low cost ~\cite{Brezmes2009}
-The experimental results show that when the sensor is placed on different rigid body, different models are required for certain activities ~\cite{Henpraserttae2011}.
-bla
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
+Energy saving on mobile devices by using different sampling frequencies \dots
 \\
@@
 We think that focusing on a high number of users by concentrating on evaluating just smartphone sensor data is significant, as the goal is to give as many people as possible access to the technology of activity recognition.
-Cell phone accelerometer data still can be enhanced by developing more sophisticated software processing sensor data and learning user behaviours, so that a basic set of gestures like walking, standing or climbing stairs can be detected mainting a low error rate while keeping the number of users at an upper level.
+Cell phone accelerometer data still can be enhanced by developing more sophisticated software processing sensor data and learning user behaviors, so that a basic set of gestures like walking, standing or climbing stairs can be detected maintaining a low error rate while keeping the number of users at an upper level.
+Although activity data is sensitive information for each individual user, it is valuable for statistical researches.
+By obtaining movement patterns of a high number of users many different insights of the world's population can be won.
+This would also contribute in improving a persons lifestyle, for example by helping him find an appropriate amount of exercise.
+As smartphones are highly connected to the internet this process can be automatized and reported to the user in real-time.
+Also comparing activity data between users might increase the willingness of people doing sports and prevent medical risks.
 

### 2018-05-25 paper/main.tex
Related work, conclusion

@@
 \section{Related Work -- Paul}
-As activity recognition is a popular topic, there already many studies and papers recording detection of gestures in both natural and laboratory settings as well as using regular mobile accelerometers and multiple high-performant accelerometers attached to different parts of the body.
+As activity recognition - especially \ac{HAR} - is a popular topic, there already many studies and papers recording detection of gestures in both natural and laboratory settings as well as using regular mobile accelerometers and multiple high-performant accelerometers attached to different parts of the body.
+
 Although the use of multiple separate acceleration sensor devices can improve results drastically up to 80\% and more ~\cite{Bao2004}, cell phones are the easiest solution to spread the capability of measuring and classifying movement patterns.
+\begin{figure}[!htb]
+\centering
+\includegraphics[width=\linewidth]{multiple_accelerometers}
+\caption{As noted by Bao and Intille ~\cite{Bao2004} this picture shows the use of five accelerometers placed on the described body parts.
+Multiple accelerometers allow more accurate detection but is also complex and only suitable in laboratory conditions when compared to mobile device accelerometers.}
+\label{fig:multipleAccelerometers}
+\end{figure}
 The use of smartphone sensors is not only practicable but also allows developing applications at low-cost ~\cite{Brezmes2009}.
+
 Cell phones however are disadvantageous to the effect that the device tilt is uncertain oftentimes ~\cite{Brezmes2009}.
@@
 Under that circumstance algorithms therefore are far more complex and their results more inaccurate.
-In one approach for instance the orientation of the 3 tri-axial sensor is used to distinguish between standing and sitting ~\cite{Kwapisz2011}, which is not a real-world scenario for everybody as every individual user might carry the phone in a different way.
+In one approach for instance the orientation of the tri-axial sensor is used to distinguish between standing and sitting ~\cite{Kwapisz2011}, which is not a real-world scenario for everybody as every individual user might carry the phone in a different way.
 As the performance of algorithms and devices have increased, the problems of phone orientation can be dealt with by now.
 Also wearing the sensor at different body parts is worsening the situation.
-Therefore a training phase combined with an AI learning algorithm can help to improve detection results ~\cite{Kwapisz2011,Bao2004}.
+Therefore a training phase combined with an \ac{AI} learning algorithm can help to improve detection results ~\cite{Kwapisz2011,Bao2004}.
 Most studies discussing activity recognition with mobile devices usually introduce training phases for collecting sensor data.
@@
 The experimental results show that when the sensor is placed on different rigid body, different models are required for certain activities ~\cite{Henpraserttae2011}.
+
 While multi-sensor approaches focus on detecting a large set of activities ~\cite{Bao2004}, many studies that make use of just one triaxial smartphone accelerometer are concentrating on a smaller subset like walking, jogging, ascending stairs, descending stairs, sitting and standing which is sufficient for detecting standard activities of most people's everyday lives.
+
 A critical point is real-time detection of gestures.
@@
 The solution of handling calculations on the mobile device is also highly scalable as no additional server is necessary for data processing ~\cite{Kwapisz2011}.
-As mobile devices nowadays are highly connective and come with additional sensors such as GPS sensors, vision sensors, audio sensors, light sensors, temperature sensors or direction sensors ~\cite{Kwapisz2011}, activity recognition offers even more possibilities.
+
+As mobile devices nowadays are highly connective and come with additional sensors such as \ac{GPS} sensors, vision sensors, audio sensors, light sensors, temperature sensors or direction sensors ~\cite{Kwapisz2011}, activity recognition offers even more possibilities.
 The availability of these technologies creates new data mining opportunities ~\cite{Kwapisz2011}.
 
-Energy saving on mobile devices by using different sampling frequencies \dots
+Energy saving on mobile devices by using different sampling frequencies, for example \ac{GPS} need a lot of power as well sensors \dots
 \\
@@
 \begin{acronym}[XXXXXXXX]
+ \acro{AI}{Artificial Intelligence}
+ \acro{GPS}{Global Positioning System}
  \acro{HAR}{Human Activity Recognition} 
- \acro{AI}{Artificial Intelligence}
 \end{acronym}
-ias
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-
-TODO Abbreviations
 
@@
 \bibliography{references}
-asdfiajsd
 %%%----------------------------------------------------------
@@
 %\bibliographystyle{ieeetr}
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-TODO Refs
-
 \end{document}

### 2018-05-25 paper/main.tex
Introduction

@@
 \usepackage{textcomp}
+\usepackage{color}
 %\usepackage[backend=bibtex,style=IEEEtr]{biblatex}
@@
 \begin{abstract}
-This document is a model and instructions for \LaTeX.
-This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
-or Math in Paper Title or Abstract.
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-TODO
+This document is a discussion on the topic activity recognition focusing on \ac{HAR} using mobile device accelerometers.
+Existing studies and papers are therefore examined and the different approaches of data collecting and processing are illustrated.
+For this work no separate experiments were carried out.
+However advantages and disadvantages of existing studies like activity recognition using a single tri-axial accelerator or using a set of multiple accelerators placed on different parts of the body are compared.
+What's more also current as well as future possibilities of \ac{HAR} concerning the health and sports sector are reflected.
+As pattern detection of different human gestures is a complex task, we concentrate on just on some main activities like walking, jogging, sitting, standing, ascending stairs and descending stairs.
+The goal is to point out aspects that apply to the majority of world's population and their most common everyday activities.
+Furthermore gesture detection involves processing power which is limited on mobile devices and also battery draining.
+Methods like configuring sampling rate in this way help saving power and optimizing the activity recognition task.
+\color{red}{*CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
+or Math in Paper Title or Abstract.}
 \end{abstract}
@@
 \section{Introduction -- Simon}
-asdfas
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-intro
+Epic intro
 

### 2018-05-25 paper/main.tex
Related work, conclusion

@@
 
-Energy saving on mobile devices by using different sampling frequencies, for example \ac{GPS} need a lot of power as well sensors \dots
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
+Similar to \ac{GPS} sensors executing gesture detection algorithms and reading accelerometer data is also battery draining for mobile devices.
+Therefore energy saving on mobile devices is an essential task.
+An human's lifestyle consists of a sequence moderately-long lasting activities.
+Saving energy can for example be achieved by using different sampling frequencies.
+The choice of both accelerometer sampling frequency and the classification features are essential ~\cite{Yan2012}.
+There are is a set of recommended frequencies for basic activities as shown in the following table:
+
+\begin{table}
+\centering
+\begin{tabular}{|c|c|}
+\hline
+\textbf{Activity} & \textbf{Smart choice} \\
+\hline
+Stand & 16Hz \\
+\hline
+Walk & 16Hz \\
+\hline
+Sit & 16Hz \\
+\hline
+Downstairs & 16Hz \\
+\hline
+Elevator up & 5Hz \\
+\hline
+Elevator down & 5Hz \\
+\hline
+\end{tabular}
+\caption{Smart choice of sampling frequencies according to Yan et al. ~\cite{Yan2012}.}
+\label{tab:smartFrequencies}
+\end{table}
+
+As stated in table \ref{tab:smartFrequencies} sampling frequencies for many basic activities like standing, walking or sitting are equal.
+This simplifies things as the sampling frequencies have to be adapted in real-time to always keep the situation optimal.
+The algorithm developed by Yan et al. ~\cite{Yan2012} shows that for users running
+the A3R application on their Android phones savings of 50\% under ideal conditions and overall energy savings of 20-25\% can be achieved.
+
 \subsection{Subsection blabla}

### 2018-05-28 paper/main.tex
Related work

@@
 The solution of handling calculations on the mobile device is also highly scalable as no additional server is necessary for data processing ~\cite{Kwapisz2011}.
+
+Concerning feature extraction different configurations chosen in the particular studies.
+Ravi et al.
+~\cite{Ravi2005} for instance collected data for a window size of about 5.12 seconds using a sampling frequency of 50Hz while Kwapisz et al.
+~\cite{Kwapisz2011} divided the data into segments of 10 seconds at sampling frequency of just 20Hz.
+Although the settings vary from each other the extracted features almost always are similar ~\cite{Ravi2005}.
+Typical features are
+\begin{itemize}
+\item mean
+\item standard deviation
+\item energy
+\item correlation.
+\end{itemize}
+
+\begin{figure}[!htb]
+\centering
+\includegraphics[width=\linewidth]{different_activities}
+\caption{A graph by Ravi et al. ~\cite{Ravi2005} showing the X-axis readings for different activities}
+\label{fig:differentActivities}
+\end{figure}
+Like figure \ref{fig:differentActivities} is suggesting activities all have a certain pattern.
+Of course these patterns can be distinguished from each other as this is a basic requirement for detecting different activities.
+Therefore activities are mapped to classes, which requires classification techniques.
+A common toolkit for classification is the Weka toolkit that was called into action in many existing studies.
+Also different algorithms of this toolkit are compared as their performance as well as accuracy differs.
+Common algorithms are ~\cite{Ravi2005}
+\begin{itemize}
+\item decision tables
+\item decision trees
+\item k-nearest neighbors
+\item \ac{SVM}
+\item naive bayes.
+\end{itemize}
 
@@
  \acro{HAR}{Human Activity Recognition}
+ \acro{SVM}{Support Vector Machines}
 \end{acronym}

### 2018-06-11 paper/main.tex
add stuff

@@
 However advantages and disadvantages of existing studies like activity recognition using a single tri-axial accelerator or using a set of multiple accelerators placed on different parts of the body are compared.
-What's more also current as well as future possibilities of \ac{HAR} concerning the health and sports sector are reflected.
-As pattern detection of different human gestures is a complex task, we concentrate on just on some main activities like walking, jogging, sitting, standing, ascending stairs and descending stairs.
+Furthermore current as well as future possibilities of \ac{HAR} concerning the health and sports sector are reflected.
+As pattern detection of different human gestures is a complex task, we concentrate just on some main activities like walking, jogging, sitting, standing, ascending stairs and descending stairs.
 The goal is to point out aspects that apply to the majority of world's population and their most common everyday activities.
 Furthermore gesture detection involves processing power which is limited on mobile devices and also battery draining.
-Methods like configuring sampling rate in this way help saving power and optimizing the activity recognition task.
-\color{red}{*CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
-or Math in Paper Title or Abstract.}
+Methods like configuring sampling rate help saving power and optimizing the activity recognition task.
 \end{abstract}
@@
 
-\section{Introduction -- Simon}
-Epic intro
+\section{Introduction}
+Human Activity Recoginition tries to harness the data of acceleration sensors in order to conclude the current activity of the user.
+The challenge is to get clearly distinguishable datasets for daily activities by using the cheapest and easiest method to acquire the data.
+One of the cheapeast methods is to use the sensors already built into todays mobile devices, instead of using different acceleremeters attached to the body.
+Additionally the mobile devices nowadays are shipped with several more sensors like audio sensors, vision sensors, location sensors, temperature sensors or direction sensors ~\cite{Kwapisz2011}.
+The combination of these different sensors can lead to different new use-cases to apply this data on, creating new opportunities for developers and users.
+Opportunities for applications to get even more ubiquous than they already are and therefore to improve life quality of the user.
+\newpage
+\subsection{The Activity Recoginition Process}
+As Su et al.
+lined out in their work, the process of recognizing an activity is typically seperated into training and testing.
+For training, data is collected for each activitiy and out of this data a classification model is created.
+When testing data is received, the classification model is used to identify the activity and hopefully recognize the correct activity.
+This process is applied in most of the works related to activity recognition.
+\begin{figure}[!htb]
+\includegraphics[width=\linewidth]{recognition_process}
+  \caption{A typical process for activity recognition with smartphone sensors by Su et al. ~\cite{Su2014} }
+  \label{fig:recognition_process}
+\end{figure}
 
-\section{Related Work -- Paul}
-As activity recognition - especially \ac{HAR} - is a popular topic, there already many studies and papers recording detection of gestures in both natural and laboratory settings as well as using regular mobile accelerometers and multiple high-performant accelerometers attached to different parts of the body.
+\section{Related Work}
+As activity recognition - especially \ac{HAR} - is a popular topic, there already many studies and papers recording detection of gestures in both natural and laboratory settings as well as using regular mobile accelerometers and multiple high-performance accelerometers attached to different parts of the body.
 
@@
 Cell phones however are disadvantageous to the effect that the device tilt is uncertain oftentimes ~\cite{Brezmes2009}.
-So sensor data for a particular movement patterns may differ from each other significantly.
+So sensor data for particular movement patterns may differ from each other significantly.
 Under that circumstance algorithms therefore are far more complex and their results more inaccurate.
@@
 
-\begin{table}
+\begin{table}[!htb]
 \centering
@@
 
-\subsection{Subsection blabla}
-subsection
+\section{Evaluation}
+Different papers discussed in the Related Works Section come to different Results depending mostly on the type of used sensors.
+Following sections will firstly show the results of cell phone accelerometers and secondly the results of a tri-axial accelerometer attached to the body.
+
+\subsection{Cell phone accellerometers}
+By using the acellerometer of a cell phone Kwapisz et al.
+came to following accuracies displayed in figure \ref{fig:accurracies_cell_phone}.
+As the graphic shows, the normal rate of recognition is over 90 percent for jogging, walking, sitting and standing.
+For going downstairs or upstairs on the other hand, the recognition tops at approximately 60 percent.
+\begin{figure}[!htb]
+  \includegraphics[width=\linewidth]{accurracies_cell_phone.png}
+  \caption{Accuracies of Activity Recoginition using cell phone acellerometers by Kwapisz et al. ~\cite{Kwapisz2011} }
+  \label{fig:accurracies_cell_phone}
+\end{figure}
 \newpage
-\section{Evaluation -- Simon}
+\subsection{Tri-axial accellerometers}
+In contrast to the results with cell phone sensors Ravi et al. came to following results displayed in figure \ref{fig:tri_axial_data}  by using a tri-axial accelerometer attached to the body.
+The confusion matrix shows the activity which was recognized when a certain activity has been done.
+There are some pretty accurate recognitions for standing, walking and going downstairs with nearly 100 percent recognition rate in each.
+Running and going upstairs contrarily don't have acurrate recognitions at all.
+\begin{figure}[!htb]
+  \includegraphics[width=\linewidth]{tri_axial_data.png}
+  \caption{Confusion Matrix for identified activities  by Ravi et al. ~\cite{Ravi2005} }
+  \label{fig:tri_axial_data}
+\end{figure}
 
-\subsection{Results}
-\begin{figure}[!htb]
+\subsection{Comparison of cell phone and tri-axial accelerometer}
+
+Comparing figure \ref{fig:accurracies_cell_phone} and \ref{fig:tri_axial_data} some key differences and similarities can be observed.
+Firstly, there is a correlation between the bad results of the activity "Upstairs".
+Using cell phone sensors, these bad results come from the similarities to going downstairs.
+On the contrary the bad results using tri-axial sensors attached to the body confuse going upstairs with running.
+One more thing that can be noticed is that "Walking" and "Standing" both have nearly perfect recognition values for both types of sensors.
+\\
+\section{Accelleration Plots for daily activities}
+As pointed out previously there are several activities that can not easily be distinguished.
+Below you can see the accelerometer profiles for some basic activities captured by Kwapisz et al.
+~\cite{Kwapisz2011}.
+The problems with wrongly recognized activities stems from the similarities in their acceleromerter profiles.
+For instance figures \ref{fig:ascendingStairs} and \ref{fig:descendingStairs} show strong similarities, which leads to the problem of wrong activity recognition.
+In contrast figures \ref{fig:walking}, \ref{fig:standing} and \ref {fig:sitting} show distinctive differences and therefore can be recognized much more accurate.\newpage
+\begin{figure}[!p]
   \includegraphics[width=\linewidth]{walking.png}
-  \caption{Walking}
+  \caption{Walking plot by Kwapisz et al. ~\cite{Kwapisz2011} }
   \label{fig:walking}
 \end{figure}
-\begin{figure}[!htb]
+\begin{figure}[!p]
+  \includegraphics[width=\linewidth]{sitting.png}
+  \caption{Sitting plot by Kwapisz et al. ~\cite{Kwapisz2011}}
+  \label{fig:sitting}
+\end{figure}
+\begin{figure}[!p]
+  \includegraphics[width=\linewidth]{standing.png}
+  \caption{Standing plot by Kwapisz et al. ~\cite{Kwapisz2011}}
+  \label{fig:standing}
+\end{figure}
+\begin{figure}[!p]
   \includegraphics[width=\linewidth]{jogging.png}
-  \caption{Jogging}
+  \caption{Jogging plot by Kwapisz et al. ~\cite{Kwapisz2011}}
   \label{fig:jogging}
 \end{figure}
-\begin{figure}[!htb]
-  \includegraphics[width=\linewidth]{sitting.png}
-  \caption{Sitting}
-  \label{fig:sitting}
-\end{figure}
-\begin{figure}[!htb]
-  \includegraphics[width=\linewidth]{standing.png}
-  \caption{Standing}
-  \label{fig:standing}
-\end{figure}
-\begin{figure}[!htb]
+\begin{figure}[!p]
   \includegraphics[width=\linewidth]{ascending_stairs.png}
-  \caption{Ascending Stairs}
+  \caption{Ascending Stairs plot by Kwapisz et al. ~\cite{Kwapisz2011}}
   \label{fig:ascendingStairs}
 \end{figure}
-\begin{figure}[!htb]
+\begin{figure}[!p]
   \includegraphics[width=\linewidth]{descending_stairs.png}
-  \caption{Descending Stairs}
+  \caption{Descending Stairs plot by Kwapisz et al. ~\cite{Kwapisz2011}}
   \label{fig:descendingStairs}
 \end{figure}
+\clearpage
 
-\newpage
-\subsection{Analysis}
-
-TODO some analysis shit
-
-\section{Conclusion -- Paul}
+\section{Conclusion}
 The use of smartphones for activity recognition is appropriate to achieve a high number of users, however it not the most accurate approach.
